Objective-first optimization for nanophotonics

### 2011-07-30 presentations/group-pres_2011-08-04.tex
Finished structure constraint section.

\oursection{Structure constraint: level-set method}
\BIT
\item a more detailed statement of our problem is
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0 \\
        & \quad p \in \{p_\text{manufacturable}\}
\end{align}
\item need to constrain possible $p$ to what can be fabricated
\item for nanophotonics this means two distinct materials only
\item however, using $p \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
\EIT
\newpage

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of a higher-dimensional function
\begin{center}
\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
source: \url{http://en.wikipedia.org/wiki/Level_set_method}
\end{center}
\EIT
\newpage

\BIT
\item ...
\begin{center}
\includegraphics[width=0.8\textwidth]{../figures/structure-progression.jpg} \\
\end{center}
\EIT

>>>>

\oursection{Structure constraint: level-set method}
\BIT
\item a more detailed statement of our problem is
\begin{align}
\mbox{decrease} & \quad \|g(x,p)\|^2 \\
\subjectto & \quad f(x) = 0 \\
        & \quad p \in \{p_\text{manufacturable}\}
\end{align}
\item need to constrain possible $p$ to what can be fabricated
\item for nanophotonics this means two distinct materials only
\item however, using $p_i \in \{\epsilon_1, \epsilon_2\}$ defeats the purpose of using linear approximations
\EIT
\newpage

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
\begin{center}
\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
source: \url{http://en.wikipedia.org/wiki/Level_set_method}
\end{center}
\EIT
\newpage

\BIT
\item updating $p(\phi)$ proceeds in the following way:
\BEQ
\phi^n \xrightarrow{\text{interp.}} \gamma 
    \xrightarrow{\text{ratio}} p
    \xrightarrow{-\pf{r}{p}} dp
    \xrightarrow{\left(\pf{p}{\phi}\right)^{-1}dp} d\phi
    \xrightarrow{\phi + d\phi} \phi^{n+1}
\EEQ
\item $\phi = 0$ defines the boundary between materials
\item boundary points $\gamma$ are linearly interpolated between adjacent $\phi$ of opposite sign
\item $p_i$ approximated by ratio of each material within cell
\item solve least-squares problem $\pf{p}{\phi} d\phi = dp$ to obtain $d\phi$
\EIT
\newpage

\BIT
\item to test, hold $x$ constant, and update $p$ 
\begin{center}
\includegraphics[width=0.6\textwidth]{../figures/structure-progression.jpg} \\
\end{center}
\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo.m})
\item new code at \url{https://github.com/JesseLu/lset-opt}
\EIT

\oursection{Example}
put it all together and let'er rip!
